PeerMind

### 2016-08-06 paper.tex
Adding various notes.

@@

% decision vs. vote vs. voting (how to name the step in decision making where you vote, and what is what you cast?)

% motion

@@

\subsection{Dynamic quroum}

@@

Because not every member of the community has time or knowledge to vote all the time, each member can delegate
decisions to one or more other members of the community.
When a member does not vote themselves, information how those delegates voted is combined into a vote of
the non-voting member.
If a delegate has not voted themselves either, their vote is computed through delegation as well, recursivelly.

@@

\begin{itemize}
\item Member $M_0$ decides not to delegate at all.
\item Member $M_1$ delegates to $M_0$ and $M_3$ with ratios $0.75$ ($r_{1,0}$) and $0.25$ ($r_{1,3}$), respectivelly.
\item Member $M_2$ delegates to $M_3$ with ratio $1.00$ ($r_{2,3}$).
\item Member $M_3$ delegates to $M_1$ and $M_2$ with ratios $0.40$ ($r_{3,1}$) and $0.40$ ($r_{3,2}$).
\end{itemize}

Observe that member $M_3$ decided to use only $0.8$ of their vote in the case they do not vote themselves.
The rest ($0.2$) counts towards non-voting population.
In this way a member can decide to participate in voting through delegation, but not fully.
Member $M_0$ deciced to not participate at all and if they do not vote they are counted towards non-voting population.

@@

To continue with our example, let's say that $M_0$ and $M_2$ voted for a decision with $0.7$ and against with $0.4$,
respectivelly.
We are using score voting on $[-1, 1]$ range, so those votes are represented with $V_{M_0} = 0.7$ and
$V_{M_2} = -0.4$.

@@

The result (average of scores) without delegation is $\overline{v} = 0.15$ and
with delegation is $\overline{x} = 0.22$.
Delegation pushes decisision slightly in favor.

@@

Solving $\mathrm{D} \mathbf{x_w} = \mathbf{w}$ and $\mathrm{D} \mathbf{x_a} = \mathbf{a}$ gives
us number of votes and number of abstentions, respectivelly, by summing together all values in the
resulting vectors: $w = \sum \mathbf{x_w}$, $a = \sum \mathbf{x_a}$.

@@

We pass computed votes and number of votes and abstaintions into computation of dynamic quorum to determine
a quorum and confidence, in the same manner as if members voted themselves.

@@

>>>>

\todo[inline]{This section is mostly notes. Organize and improve.}

@@

\todo[inline]{Terminology: decision vs. vote vs. voting (how to name the step in decision making where you vote, and what is what you cast?)}
\todo[inline]{Terminology: motion? Tally? What is the sum of all votes?}

The main question is: can we increase legitimacy and decrease attention required at the same time.
Many others are trying to increase attention (participation) because they want to increase legitimacy,
assuming that this is the only way.

A list of potential other points:
\begin{itemize}
\item legitimacy (quorum, involvement of more people through delegation)
\item scaling (delegation helps, less attention helps)
\item attention (at same or better decisions)
\item bad assumptions for democracy - time, knowledge, it s rational to know that you do not know, common practice is to ask friends
\item better decisions (more people consulted, attention directed where it should be)
\end{itemize}

Another question: should feedback be visible (to see how others voted before you voted)?
People go with majority.
Better for wisdom of crowds is an independent sample.
Maybe we should only allow how other voted to be seen after you voted ()but you can still change the vote),
but we could then observe that and learn from this and see if this is good or bad.
Or we could just store information if you observed existing votes before you voted (you have to click a button to see them).
Maybe going with majority is also good when you want more social cohesion in the community and not so much "optimal"
wisdom of crowds result -  you would want that people relax their positions based on how other people care.
Cohesion of the group vs. accuracy.
Maybe display only number of votes and confidence, maybe confidence direction or graph, but not average votes.

A list of potential questions:
\begin{itemize}
\item Delegation works?
\item Statistical quorum works?
\item Real-time feedback influences?
\item Private vs. public delegation (do you know how member to whom you delegated is voting)?
\item Knowing how much power you have vs. not knowing -- does it change how people behave? (Knowing might corrupt you, but also motivate you to do more thorough work voting because you know other depend on you.)
\end{itemize}

Performance/theory/scaling in terms in computational (how big could effectively community can be to be able to compute it).
Some other theoretical properties?

@@

\subsection{Dynamic quorum}

@@

Because not every member of the community has time or knowledge to vote all the time, each member can delegate
decisions to one or more other members of the community.
When a member does not vote themselves, information how those delegates voted is combined into a vote of
the non-voting member.
If a delegate has not voted themselves either, their vote is computed through delegation as well, recursively.

@@

\begin{itemize}
\item Member $M_0$ decides not to delegate at all.
\item Member $M_1$ delegates to $M_0$ and $M_3$ with ratios $0.75$ ($r_{1,0}$) and $0.25$ ($r_{1,3}$), respectively.
\item Member $M_2$ delegates to $M_3$ with ratio $1.00$ ($r_{2,3}$).
\item Member $M_3$ delegates to $M_1$ and $M_2$ with ratios $0.40$ ($r_{3,1}$) and $0.40$ ($r_{3,2}$).
\end{itemize}

Observe that member $M_3$ decided to use only $0.8$ of their vote in the case they do not vote themselves.
The rest ($0.2$) counts towards non-voting population.
In this way a member can decide to participate in voting through delegation, but not fully.
Member $M_0$ decided to not participate at all and if they do not vote they are counted towards non-voting population.

@@

To continue with our example, let's say that $M_0$ and $M_2$ voted for a decision with $0.7$ and against with $0.4$,
respectively.
We are using score voting on $[-1, 1]$ range, so those votes are represented with $V_{M_0} = 0.7$ and
$V_{M_2} = -0.4$.

@@

The result (average of scores) without delegation is $\overline{v} = 0.15$ and
with delegation is $\overline{x} = 0.22$.
Delegation pushes decision slightly in favor.

@@

Solving $\mathrm{D} \mathbf{x_w} = \mathbf{w}$ and $\mathrm{D} \mathbf{x_a} = \mathbf{a}$ gives
us number of votes and number of abstentions, respectively, by summing together all values in the
resulting vectors: $w = \sum \mathbf{x_w}$, $a = \sum \mathbf{x_a}$.

@@

We pass computed votes and number of votes and abstentions into computation of dynamic quorum to determine
a quorum and confidence, in the same manner as if members voted themselves.

@@

\subsection{Three step process}

\subsection{Real-time feedback}

% Real-time communication in general.
